A short overview of the report where one can read what the different chapters contain

\section*{Chapter 1}
Introduction to the project explaining how human makes decision and how a computer would make decisions. This part also explains the purpose of this project, and what kind of problem we would like to solve.
\section*{Chapter 2}
Here we explain the basic rules of the game, what is important to obtain to win a match and how one can win over an opponent. We mention some different areas of the game one has to master to be good or even perfect to win, we also mention some different standard attack methods one can use to slow down the opponent. At last we analyse what kind of unit we want a computer to control.
\section*{Chapter 3}
The design part is about different design methods one can use to control several units on a map, to avoid obstacles and still be drawn to the opponent. The last part is about the theory of agent learning what different kinds we have looked upon.
\section*{Chapter 4}
This chapter is where the theory is being used in practice, and here we explain how we have implemented the potential fields, and how we have implemented the learning part of the agent.
\section*{Chapter 5}
This chapter have the purpose to test our bot. We do this by having three test where each test is run on two different maps. The first test is the case
where the enemy attack the vultures without the vultures being controlled. This gives an idea of how strong the two forces are comparet with each other. The next test is the improvements our bot will have by using potential fields. The last test is about our bots ability to learn by using reinforcement learning.
\section*{Chapter 6}
This chapter is where we will conclude the impact the machine intelligence have had on our bot and the results we have gathered from our bot.
\section*{Chapter 7}