\section{Game Scenario}
	In this section we will describe a basic game scenario.
	
	\subsubsection{Early game}
		All players begins with four workers (SUV's) and the main building (Command Center).	The players will begin by mining minerals and will continue to do this for the entire game. At the same time the players will build more SUV's and begin to implement their build orders. 			Early in the game the player will take a SUV or an early attack unit, possibly marine, and begin to scout the map for information on the other player. 
		While scouting the player continues to expand their base with more buildings and may begin to build a second command center close to more minerals. The play could also launch a small attack on the enemy.
		
		When the scouting units find another player they will try to stay alive for as long as possible to give the player the best insight into what the other player is planning. Based on the information received the player will adjust his strategy to counter in the best possible way.
		
		A player can also choose to harass his opponent to set the enemy back.
		
	\subsubsection{Mid game}
		In mid game, the player will hope to use the information from scouting, build tech two units, and try to launch attacks against the enemy. He also needs to defend his own base while constantly trying to adapt his strategy to counter the enemy.
		
		While doing all this the player also need to expand with more bases to get a constant flow of minerals. The player may also do some harassment to delay the economy or army size of his opponent.
		
	\subsubsection{Late game}
		At this point its all out war. The earlier game hopefully gave you enough of an advantage by giving a better army composition or army size to take out your opponent. This generally escalates into one very massive batter of extremely strong armies.