\section{Unit Analysis}
We will now take a look at three Terran units which could be interesting to micro. In the analysis of the units we will
focus on the range, movement speed, damage, armor, availability, micro benefits, and fire cooldown. We focus on availability because we don't want a unit we can't use in the beginning because the opponent can
win with an early attack. Micro benefits are the benefits the unit will have from micro. For example since the siege tank has a static position when it is in siege mode, so we can't get much benefit from microing
this unit. 

\subsection{Marines}
Marines are interesting because they can shoot air and ground units. The upgrade stimpacks increases the marines movement speed and the fire rate
faster from 7.5 to 15. This makes the unit very dynamic and gives it high micro benefits. Marines are easy to get and are normally the first unit a Terran uses in
their army. Marines only have a range of 4 and are the slowest unit that we are going to take a look at. There
hit points are only 40. Since marines can be gotten so early on they are a good candidate for the project. On the other hand, to get the full profit from the
marines they need upgrades and support from medics to heal them. 

\subsection{Vultures}
Vultures are a little car with a high speed, a range of 5 and 80 hit points. This means a vulture can out micro a marine. Like the marines, the
vultures also have upgrades. The most interesting upgrade is the spider mines that allows the vultures to place three mines. When another unit goes near the mine it will detonate dealing a large amount of splash damage. The vultures are made
from the Factory which means you will be able to get marines before you get vultures. The good thing about vultures is the prize is only 75 minerals (where
a marines is 50 minerals). Having all this in mind, it is clear that vultures have much to offer in terms of micro.
That being said the vultures fire cooldown is 30 fps which is double the time of the cooldown of a marine.

\subsection{Wraiths}
Wraiths are air units that can attack ground and other air units. This means that they are not depended on surroundings which allows it
to move over large distances within a short time. They are interesting because they have a upgrade that allows them to turn invisible while they have energy. Wraiths 
have a range of 5, and have 120 hit points which is 3 times more then a marines. It has the same fire cooldown
as a vulture when attacking ground units and 22 fps when attacking air units.  
The down side of the wraiths is the price( 150 minerals and 100 gas) and we need a Starport to built it. This means
there is a long time before you can get actually buy wraith. It is clear there is a lot of micro benefits from choosing this unit. 


\subsection{Conclusion}
As said before the vultures, with its fast speed and long range, could be a interesting unit to choose because the vulture can out micro many types of
units. It will be easy to deal a lot of damage with the use of multiple attacks and the fast movement speed making it a very dynamic unit. Also the vulture
is not dependent on other support units like medic. If the vulture is low on health, it can just return back to the base and get repaired. This means
only one unit type is needed to be controlled. Of cause the down side is the vultures only can attack other ground units like it self. Another down side
is the slow fire cooldown compared to the marine, but this only means that it will take longer time to kill marines.\\
If we like to have a fast unit that can fly, like the wraiths, we need to keep in mind that we are very vulnerable in the beginning. This means it is very
easy for the opponent to win if he scouts our base. Because it is normal to scout in the beginning of the game we are already weakened. So it is clear that
the wraiths could be a interesting and strong unit to micro, but not as a stand alone unit. We can therefore conclude the best micro unit from the three cases is the vulture.