\section{Bot Managers}
	\label{design::managers}
	The managers for the bot are used to control different parts of the bot. The part which is connected to the micromanaging of units will use 
	reinforcement learning and Potential fields. The part which manages scouting information will use Bayesian networks. 
	The purpose for these managers are to separate parts of the game as much as possible. They should only use the other managers when a task needs to be handled 
	by another manager. The following subsections will explain the different managers.
	
	\subsection*{Tactics Manager}
		This manager is responsible for managing our offensive units in and out of small scale combat. 
		It manages the units by controlling squads of different units.
	\subsection*{Production Manager}
		This manager is responsible for producing units, constructing buildings, upgrading technology and researching technology. The manager will be able to 
		know what to build by following build orders.
	\subsection*{Scouting Manager}
		The Scouting Manager keeps track of the opponent. 
		It saves every enemy it has seen and is responsible for scouting the enemy's spawn position. 
		It also keeps track of which buildings the enemy has produced.
	\subsection*{Strategy Manager}
		The Strategy Manager is responsible for making high-level decisions based on the information we have. These decisions include
		setting the Tactics Manager to attack the enemy or setting the Production Manager to change build order.
	\subsection*{Worker Manager}
		The Worker Manager sets the workers to mine minerals, mine gas, scout, construct buildings and perform other tasks.
	\subsection{Managers in Game Scenario}
		
		The game starts and the Production Manager begins following the build order which produces SCVs. Every time an SCV is created the 
		Worker Manager sets the worker to a free mineral patch. The Scouting Manager sends out an SCV to the opponent's base. The scout 
		finds the base and the Strategy Manager still predicts that the threat level is low. The Production Manager keeps following the build order, and now 
		we have marines assigned to a Tactics Manager. The Scout Manager sends out another SCV, but this one is killed before reaching the base of the 
		opponent. The Strategy Manager sets the threat level to high and makes the Production Manager stop producing workers. The production manager will then start producing only offensive units. 
		The opponent does the attack, and the Tactics Manager micromanages the units which defeats the enemies.
