\chapter{Design}\label{design}
	In this chapter we will distinguish between the word agent and bot, where an agent is a program thats able to learn and chance itself, and the bot it the more static.
	
	In this chapter we are going to look at the designing the bot. First we will take a look at the different managers we use for controling units, produce bulding, scouting and choose a strategy. Then you are going to explain potentialfields, and how we use it to microing the bot. Inorder to correct the bot and make sure the it will be able to learn, we will explain reinforcement learning. For the macro part we are going to use Bayesion Networks to be able to detect the opponent's build order, predicting the opponent's start location and the threat level of the opponent based on the units the bot scout.	\\
	The purpose of the design is to make an agent that able to out micro opponent in combat, to limit the scope we will only look at vultures. 
	This implies the following:
	\begin{itemize}
		\item Construct the necessary buildings to produce vultures.
		\item Construct a squad of vultures.
		\item Scout and find the enemies base.
		\item Move the squad to the enemies base and attack.
	\end{itemize}
	
%	Potential fields are a vector based representation of an environment. Potential fields are commonly used in robotics to guide a robot trough environment, but it is also becoming more and more popular within computer games\ref{ptf_in_game}. Objects in this environment can change position and the field will adapt accordingly. 
	\input{\ChapterDocsPath/chapter3-design/managers}
	\input{\ChapterDocsPath/chapter3-design/potentialfields}
	\input{\ChapterDocsPath/chapter3-design/potentialfieldsparameters}
	%\input{\ChapterDocsPath/chapter3-design/potentialfieldconclusion}
	\input{\ChapterDocsPath/chapter3-design/reinforcementlearning}
	\input{\ChapterDocsPath/chapter3-design/Bayesian-Networks-and-decion-threes}
	\input{\ChapterDocsPath/chapter3-design/bayesiannetwork}
	\input{\ChapterDocsPath/chapter3-design/DesignConclusion}
