\section{Bot Managers}
	\label{design::managers}
	The managers of the bot are meant to control different parts of the bot. The part which is connected to microing of units will be we using the 
	reinforcement learning and potential fields and the part which manages scouting information will using the Bayesian networks. 
	The idea of these managers are that they are separated as much as possible and only using the other managers when a task is needed to be handled 
	by another manager. The following subsections will explain the different managers.
	
	\subsection*{Tactics Manager}
		This manager is responsible for managing our offensive units in and out of small scale combat. It manages the units by managing squads of different 
		units.
	\subsection*{Production Manager}
		A manager which is responsible for producing units, buildings, upgrading tech and research tech. The manager will be able to 
		know what to build by following build orders.
	\subsection*{Scouting Manager}
		The Scouting Manager keeps track of the opponent. It saves every enemy it have seen and is responsible for scouting the enemy's spawn position and 
		what they are building.
	\subsection*{Strategy Manager}
		A manager which is responsible for taking the right high-level decisions based on the information we have. These decisions can be like 
		setting the Tactics Manager to attack the enemy or set the production manager to change build order.
	\subsection*{Worker Manager}
		This manager sets the workers to work at either mining minerals or gas, scouting, construction of buildings or another task.

	\subsection{Managers in Game Scenario}
		The game starts and the Production Manager starts following the build order which starts with producing of SCVs. Every time a SCV is created the 
		Worker Manager sets the workers to a free mineral patch. The Scouting Manager sends out a SCV for scouting the opponents base. The scout 
		finds the base and the Strategy Manager still predicts that the threat level is low. The Production Manager still follows the build order and now 
		we got marines assigned to a Tactics Manager. The Scout Manager send out another SCV, but this one is killed before reaching the base of the 
		opponent. The Strategy Manager sets the threat level to high and this makes the Production Manager stop producing workers and only offensive units. 
		The opponent are doing an attack and the Tactics Manager is microing the units, which defeats the enemies.
