\section{Future Work on Potential Fields}
	If we had more time to work on the potential fields they could use a lot of adjustments. They work well for our test case against the marines, but when used in most normal maps during a real game they need to take a lot more things into account. An example would be buildings, right now they are not mapped in the potential field, so the units will not take them into account only choose not to move directly on top of them due the the tile being invalid. The same goes for mineral patches and gas geysers. \\
	
	We could look into adding more potential field for all kind of scenarios, for low health etc. This should make the bot even more cleaver but it would also mean more variables to learn and we would need to relearn all the other variables. The low health vultures should be repaired by a SVN, which mean that
a SVN should stop mining\\
	
	Another thing to look at would be using a different set of forces for different scenarios, like defending the base and attacking other bases. And learning different numbers for different kind of units. There should not be anything in the way of using the potential field on other kind of units. \\
	
	We could also use more time adjusting the constants we filled in our selves\footnote{Size of the squad, minimum distance to ally and maximum distance to the edges}, to try and see what works best. \\

	As we later found out the vultures have a movement speed upgrade, this could be interesting to test the effect the upgrade would have on the
variables in reinforcement learn.	