
\section{Managers}
	A manager is responsible for controlling different sections of the bot. Sometimes they still have to pass tasks to each other. Each manager has 
	a method called Update which is called on each frame and is used for running their code.
	\subsection{Production Manager}
		The production manager is responsible for producing units, constructing buildings, and researching tech. Every time a new production facility or 
		 research facility is produced it will be saved here, so we are can use them later. 
		The tasks that the production manager is responsible for are passed from a 
		class called BuildOrderHandler.
		\subsubsection*{BuildOrderHandler}
			This class contains the build orders the bot can use and passes the items as tasks for the production manager. A BuildOrder contains a list of 
			BuildOrderItems which every class that inherits from this class can use. The items the build order can store are:
			\begin{itemize}
				\item BuildingItem - Contains a building to be constructed
				\item ProductionFocusItem - Contains a new Production Focus
				\item ResearchItem - Contains a research tech that needs to be bought
				\item UpgradeItem - Contains an upgrade that needs to be bought
				\item ScoutItem - Sends an SCV to scout
				\item UnitProductionItem - Contains a unit to be produced
			\end{itemize}
			In the constructor each these items conditions will be placed so the item first will get carried out when the condition is fulfilled.
			The conditions we have are: 
			\begin{itemize}
				\item SupplyCondition - Is fulfilled when the supply is reached
				\item ThreatLevelCondition - Is fulfilled when the threatlevel is reached
				\item UnitProductionCondition - Is fulfilled when the number of units or buildings reaches the number specified
			\end{itemize}
			The following code snippet shows the main loop of the BuildOrderHandler which goes through the items in the build order and checks if the 
			conditions are all fulfilled.
			\pagebreak
				\begin{Sourcecode}[caption=BuildOrderHandler main loop]
		std::list<BuildOrderItem*> items = _currentBuildOrder->GetBuildOrderItems();
		(*@\lnote@*)for(std::list<BuildOrderItem*>::iterator item = items.begin();item!=items.end();++item)
		{
			bool allConditionsFulfilled = true;
			std::list<Condition*> conditions = (*item)->GetConditions();
			for each(Condition* condition in conditions)
			{
				if(!condition->IsFulfilled())
				{
					allConditionsFulfilled = false;
					break;
				}
			}
			//If all the conditions of the item was fulfilled we save it to the right list of tasks
			if(allConditionsFulfilled == true)
			{
				SaveAsTask(*item);				
				_currentBuildOrder->items.remove(*item);
			}
		}	
				\end{Sourcecode}
			This loop grabs the BuildOrderItems in the current buildorder and in the loop at \lnnum{1} we check if all the conditions of the item were 
			fulfilled. Each condition object inherits from the class Condition where they inherit a method called IsFulfilled. Each condition that 
			overrides the method has to specify when the given condition will be fulfilled. If all the conditions were fulfilled, we convert the 
			item to a Task and save it so the ProductionManager can retrieve the Task. The difference between a BuildOrderItem and a Task is that the 
			item is stripped of all information except the information that is important in producing the task. 
			
		\subsubsection*{Retrieving and executing tasks}
			The ProductionManager contains methods for retrieving tasks from the BuildOrderHandler. There is a method for each type of task it can 
			produce. When it has retrieved all the tasks it tries to see if it can execute it right away. 
			If we can afford to do the task it will be passed on to the appropriate method for execution. These 
			methods are called TryProduceUnit, TryConstructBuilding, TryUpgradeTech, and TryResearchTech. There is a method for both upgrades and 
			researching because the BWAPI makes a distinction between these two types. The methods all follow the same basic 
			pattern.
			\begin{itemize}
				\item Check if we can afford the task
				\item Find a building that can execute the task
				\item If both succeed the task will be executed
			\end{itemize}
			The only method that does not follow this pattern is the method TryConstructBuilding. The reason for this is that the ProductionManager is not 
			able to construct a building without an SCV. Because of this we pass this task on to the WorkerManager that will try to construct the building.
			
	\subsection{WorkerManager}
		This manager controls the SCVs the bot owns and is responsible for constructing buildings. When an SCV is created it is saved to a list of 
		SCVs and is given a state. An SCV can be in one the following states: Constructing, BeingBuild, MiningGas, MiningMinerals, Defending, Evading, or Nothing. When 
		the SCV is completed from the Command Center it will get the state Nothing. The Update method will then determine what the SCV should do. Usually 
		the SCV will be set to mine minerals, so it gets the state MiningMinerals. 
		\subsubsection*{Efficient mining}
			To ensure that the bot will get the most minerals in relation to how many SCVs it has, we have implemented a way to mine more efficiently by choosing the right mineral or refinery to mine from. The following code snippet is from the method SendToMineral, which sends a single SCV
			to a mineral patch.
			
				\begin{Sourcecode}[caption=SendToMineral method]
	int fewestScvs = 100;
	int distanceToMineral = 10000;
	BWAPI::Unit* bestMineral;

	(*@\lnote@*)for(std::map<BWAPI::Unit*,int>::iterator m = _workersOnMineral.begin();m != _workersOnMineral.end();m++)
	{
		if((*m).second < fewestScvs)
		{
			fewestScvs = (*m).second;
			bestMineral = (*m).first;
			distanceToMineral=scv->getDistance(bestMineral);
		}
		else if((*m).second ==fewestScvs && scv->getDistance((*m).first)<distanceToMineral)
		{
			fewestScvs = (*m).second;
			bestMineral = (*m).first;
			distanceToMineral=scv->getDistance(bestMineral);
		}
	}
	(*@\lnote@*)_workersOnMineral[bestMineral]++;
	_scvResourceGoals[scv]=bestMineral;
	scv->rightClick(bestMineral);
				\end{Sourcecode}
			Each mineral patch and refinery are mapped to an int which represents how many SCVs are using this patch or refinery. To find the best mineral 
			patch every mineral patch we are mining from is iterated through \lnnum{1} and checked if there are less SCVs than the preceding mineral patch. 
			The distance to this mineral patch is also saved because there might be a mineral patch which has as few SCVs on the patch but is closer. 
			When the best mineral patch is found it is noted\lnnum{2} that an additional SCV is working on that mineral patch- After this we save the 
			mineral to the SCV and sends the SCV to mine the mineral patch by right clicking it.
			
		\subsubsection*{Constructing buildings}
			Below is the code that the Production Manager calls when it has a ConstructionTask that needs to be executed. The method is called 
			ConstructBuilding and has the parameters of type UnitType and BuildingPlacement, where BuildingPlacement 
			is an enum that can have the values MainBase or MainChokepoint.
			\pagebreak
			\begin{Sourcecode}[caption=ConstructBuilding method]		
	(*@\lnote@*)BWAPI::TilePosition position = finder.FindBuildLocation(buildingType,placement);

	(*@\lnote@*)BWAPI::Unit* scv = GetAvailableScvNearPosition(BWAPI::Position(position.x(),position.y()));
	

	(*@\lnote@*)SwitchState(scv,WorkerManager::Constructing);
	
	(*@\lnote@*)buildingToConstruct building;	
	building[position] = buildingType;
	_workersOnConstruction[scv] = building;
	scv->build(position,buildingType);
			\end{Sourcecode}
			
			To find a location to place a building we use an instance of the class BuildingPlacementFinder called finder (see \lnnum{1}).
			This class can find a suitable location for a building to be constructed in relation to the enum specified. After this we find an SCV for the 
			task \lnnum{2} by using the method GetAvailableScvNearPosition which gets the nearest scv that is not carrying minerals, mining gas, or 
			constructing buildings. With the position and an SCV the building can now be constructed. The state of the SCV is changed to Constructing \lnnum{3}, and 
			we save the building information, so we are able to try again if it fails in constructing the building. \lnnum{4} is a type containing 
			a map between a position and a building type. After this the SCV tries to 
			construct the building.
	\subsection{Scouting Manager}
		The scouting manager is used to find the opponents base and obtain information on what the opponent is doing. 
		It uses a Bayesian network to find the most probable location for the enemy base.
		At the beginning of the match evidence is instantly inserted on the "OurSpawn" node of the Bayesian network.
		Whenever an opponent's worker is found, evidence for the worker location and current game time are placed as evidence in the 
		Bayesian network and our scout is sent to the new most probable worker location. 
		Once the scout finally finds the opponent's base, it gathers information on which 
		buildings the opponent has in order to help predict the build order.
	\subsection{Strategy Manager}
		This manager was supposed to be responsible for making high level decisions for the bot, but we have not finished the manager completely. We have made the necessary analysis needed to make these prediction. By using the class BuildOrderPredictor we are able to retrieve the most 
		probable build order and threat level.
		
		\subsubsection{Build Order Predictor class}
			This class uses a Bayesian network to analyze what build order the enemy is currently doing. This is related to the current threat level which
			the strategy manager retrieves. \\
			
			The class is instantiated by loading the proper prediction network in relation to the match up and saving the match up as a variable. 
			The class have a public method for updating the prediction network which then calls the proper method for updating the correct network related 
			to the current match up. The nodes in the Bayesian network have similar names, so that the conversion from the unit type to the node name can be 
			done more easily. When an enemy unit is scouted the strategy manager passes this to the BuildOrderPredictor which then tries to put evidence 
			on the correct node. Such a conversion can be seen below.
			\begin{Sourcecode}[caption=Conversion from unit type to node name]		
	if((building == BWAPI::UnitTypes::Terran_Academy || 
			building == BWAPI::UnitTypes::Terran_Starport ||
			building == BWAPI::UnitTypes::Terran_Barracks ||
			building == BWAPI::UnitTypes::Terran_Factory)&& 
			enemyBuildingsOwned[building]==1)
	{
		//Converts the building type to how the nodes are written
		std::string nodeName = building.getName();
		nodeName.erase(0,7);
		std::remove(nodeName.begin(), nodeName.end(), ' ');
		char buffer [2];
		std::string nodeNumber = itoa(1,buffer,10);	
		predictionNetwork.EnterEvidence((nodeName+nodeNumber),"Seen");
		BWAPI::Broodwar->printf("Updated the prediction network");
		predictionNetwork.PrintMostProbableState("BuildChosen");
	}
			\end{Sourcecode}
			 The code removes Terran string and the white spaces and saves it to a string. The number of buildings of the type is converted to a string too. 
			 Then the evidence is entered and prints the most probable build order.
	\subsection{Tactics Manager}
		The TacticsManager is responsible for managing the offensive units the bot owns. When units of the same type are near each other they are saved 
		to a Squad object. The TacticsManager executes all the tactics of the Squad objects in it's Update method. This tactic that the squad executes 
		are from the Reinforcement Learning and Potential fields which will be explained in the next sections.
		
			
		
			
			
				
			
		
