\section{Game Scenario}
	In this section we will describe a game scenario.
	
	\subsubsection{Early game}
		All players begins with four workers (SUV's) and the main building (Command Center).	The players will begin by mining minerals and will continue to do this for the entire game. At the same time the players will build more SUV's and begin to implement the building order. 			Early in the game the player will take a SUV or one of the early attack units, possibly marine, and begin to scout the map for the other's play. 
		While scouting the player continues to expand their base with more buildings and maybe begin to build a second common center close to more minerals or maybe launch a small attack on the enemy.
		
		When the scouting units find another player they will try to stay alive for as long as possible to give the player the best insight into what the other player is planning. Based on the information received the player will adjust his strategy to counter in the best possible way.
		
		A player can also choose to due some harassment moves to set the enemy back.
		
	\subsubsection{Mid game}
		In mid game, the player will hope to draw benefit of the scouting, building tech two units, and try to launch attacks against the enemy, and defending his own base while constantly trying to adapt his strategy to counter the enemy.
		
		While doing all this the player also need to expand with more bases to get a constant feed of minerals, and maybe doing some more harassing.
		
	\subsubsection{Late game}
		At this point its all out war, trying to defeat the other players by, hopefully, haven chosen the better strategy, or by macroing you way to victory.