\section{Terran tactics}
	This section will feature some more concrete ways of winning a game as a Terran player. 
	These tactics are important to analyze because a bot will need to know these tactics in order to win.
	The following subsections are tactics, which can win a game when playing as Terran.
	
	\subsection{Timing Push}
		A timing push is an attack which either hits when a specific upgrade is done, and/or when the opponent is vulnerable in his specific build order. 
		Because a bot can be very precise a timing push can be deadly. Making the bot attack when a specific upgrade should be trivial to do, but for it to 
		analyze when the opponent is weak may be a more difficult task. This would require the bot to research which build order the opponent is using and 
		then change its build order or strategy to fit a timing attack. If the bot could succeed in doing this, it would take opponents off guard.
		
	\subsection{Pushing}
		The term \textit{pushing} refers to an attack which finds place when the Terran player has gained a large army after being defensive for a long 
		period of time. It is called pushing because the idea is to push the opponent 
		all the way back to their base where they will deal the finishing blow. This is a Terran tactic which is very easy to execute because it is generally
		easy to defend your base as Terran. When you are ready to do the push your army will be difficult to beat.
		
	\subsection{Harass}
		Harassing is a tactic that every race can use, but here we will give some ways for the Terran race to do it. Doing drops is one way to harass, Dropping 
		refers to transporting units into the opponents base. The most common type of drops for Terran are done with vultures and marines. The vultures are 
		fast and can take out the workers in the base. They can also place mines so enemy units can not easily come to defend the workers. When dropping with marines 
		the purpose is generally just to destroy important enemy buildings rather than kill workers(note this is not always the case). Vultures can also be used without 
		dropping them. Because of their superior speed vultures can easily slip past enemy units and into the enemy's main base. Doing harassment requires 
		good multitasking ability. If you keep your units out of sight for one second they might be destroyed, and if you forget to macro you can 
		get far behind economically. This is a field that the bot can really show its abilities because multitasking is something that is hard for a human to do but 
		easy for a computer.
	
	\subsection{Mining the map}
		In this tactic vultures are used to gain map control by placing mines all over the map. If the opponent wants to attack he will need to destroy the 
		mines. This can give the Terran player security and a way to establish a superior army and economy. 
		This is also a tactic that requires a lot of multitasking and is quite closely related to the harassment tactic because they both act in a 
		aggressive way.
		
	
		
		
		