\section{Unit Analysis}
We will now take a look at three Terran units, which could be interesting to micro. In the analysis of the units we will
focus on the following properties range, movement speed, stats, availability and micro benefits. The units stats are damage
and armor. We focus on availability because we don't want a unit we can't use in the beginning, because the opponent can
win with a early attack. Micro benefits are the benefits the unit will have from micro and how easy it will be to out micro
other units. For example the siege tank have a static position when it is in siege mode, so we can't get any benefits for microing
this unit. 

\subsection{Marines}
Marines are interesting because they can shoot air and ground units. The upgrade stimpacks makes the marines very fast and makes the fire rate
faster. This makes the unit very dynamic and have high micro benefits. Marines are easy to get and is normally the first unit Terrans use in
the army. Marines only have a range of 4 and is the slowest unit that we are going to take a look at. There
hit points are only 40. Keeping the prize in mind and the fact that marines don't require a lot of
technological buildings, makes the marine a good candidate. On the other hand, to get the full profit from the
marines it needs upgrades and the support from medics to heal them. 

\subsection{Vultures}
The vultures are a little car with high speed, range of 5 and 80 hit points. This means a vulture can out micro a marine. Like the marines, the
vultures also have upgrades. The most interesting upgrade is the spider mines that allows the vultures to place three mines. The vultures is made
from the Factory, this means you will have marines before you get vultures. The good thing about vultures is the prize is only 75 minerals (where
a marines is 50 minerals). Having all this in mind, it is clear that the vulture have many micro benefits and could be a very strong unit to micro. 

\subsection{Wraiths}
Wraiths are air units that can attack ground and other air units, this means that they are not depended on surroundings and thereby allows it
to move over large distances within short time. They are interesting because they have a upgrade that allows them to be invisible. The wraiths 
have a range of 5, which is the same as a vulture, and it have 120 hit points, which is 3 times more then a marines.
The down side of the wraiths is the prize( 150 minerals and 100 gas) and that we need a Starport to built it, this means
there gos a long time before you can get a wraith. It is clear there is a lot of micro benefits from choosing this unit. 


\subsection{Conclusion}
As said before the vultures, with its fast speed and long range, could be a interesting unit to choose because the vulture can out micro many types of
units. It will be easy to deal a lot of damage with the use of multiple attacks and the fast movement speed makes it a very dynamic unit. Also the vulture
is not dependent on other support units like medic. If the vulture is low on health, it can just return back to the base and get repaired. This means
only one unit type is needed to be controlled. Of cause the down side is the vultures only can attack other ground units like it self.\\
If we like to have a fast unit that can fly, like the wraiths, we need to keep in mind that we are very vulnerable in the beginning. This means it is very
easy for the opponent to win, if he scouts our base. Because it is easy to scout in the beginning of the game, we are already weakened. So it is clear that
the wraiths could be a interesting and strong unit to micro, but not as a stand alone unit. We can therefor conclude the best result, from the three cases
we have looked at, the vulture is the strongest choose.