In this project we look at Starcraft Broodwar which is a \abrts game and Machine Intelligence. Starcraft Broodwar is interesting in relation to look at for several reasons, it requires as much strategy as chess, it has the unknown aspect of poker, and its as unpredictable as scrabble. These three factors makes it an ideal game for Machine Intelligence.

Another advantages of Starcraft Broodwar is that its easy to learn but hard to master. The basic of the game is very simple can be understood in a matter 30 minutes, but to become a true professional take years of intensive training. Which is great for Machine Intelligence since we can easily teach a computer to play the game, but making it good will be hard work.\\

Using a computer to play Starcraft Broodwar is interesting in the sense that computer exceeds humans in more then one area. It will be able to do many advanced calculation during a game, and be able to control the mouse and keyboard very rapidly manner. Especially the mouse and keyboard movement opens the door for some interesting opportunities, a human can only control a limited about of units or buildings a one time, but a computer would be able to control all of them. \\

Machine Intelligence is interesting in relation to Starcraft Broodwar because we would be able to take a subset of the game, and really focus on that part, and train the computer to do that one part just right each time. Which could be
\begin{itemize}
	\item Teach it to use just the right strategy at the right time.
	\item Predict what the other players are during.
	\item Teach it to control single units in just the right way.
\end{itemize}

All the above part truly makes Starcraft Broodwar an interesting game to look at with a lot of different options for the main focus of the remainder of this report.

\section{Purpose}

	The purpose of this project is to create a computer program that is able to play a full game of Starcraft Broodwar. But also showing the advantages of using a computer by making it due tasks that would be impossible for a human being. It shold be able, trough trials, learn from its mistakes and become better using machine intelligence theory. 


\section{Problem Statement}
	Our goals for this project is to:
	\begin{itemize}
		\item Create an intelligent bot for the game Starcraft Broodwar
		\item Apply machine intelligence theory in the modeling of the bot
		\item Make a bot that can improve by playing Starcraft
	\end{itemize}

\section{Overview}
	A short overview of the report where one can read what the different chapters contain

\paragraph*{Chapter 2 - Analysis}
Here we explain the basic rules of the game, what is important to obtain to win a match and how one can win over an opponent. We mention some different areas of the game one has to master to be good or even perfect to win, we also mention some different standard attack methods one can use to slow down the opponent. At last we analyze what kind of unit we want a computer to control.
\paragraph*{Chapter 3 - Design}
The design part is about different design methods one can use to control several units on a map, to avoid obstacles and still be drawn to the opponent. The last part is about the theory of agent learning what different kinds we have looked upon.
\paragraph*{Chapter 4 - Implementation}
This chapter is where the theory is being used in practice, and here we explain how we have implemented the potential fields, and how we have implemented the learning part of the agent.
\paragraph*{Chapter 5 - Tests}
This chapter have the purpose to test our bot. We do this by having three test where each test is run on two different maps. The first test is the case
where the enemy attack the vultures without the vultures being controlled. This gives an idea of how strong the two forces are compared with each other. The next test is the improvements our bot will have by using potential fields. The last test is about our bots ability to learn by using reinforcement learning.
\paragraph*{Chapter 6 - Future Work}
This chapter is where we will conclude the impact the machine intelligence have had on our bot and the results we have gathered from our bot.
\paragraph*{Chapter 7 - Conclusion}
